Homicide Increases in the COVID-19 Era

### 2025-02-27 Draft1.qmd
echo False

## Number of Evictions and Crime Levels Per Month
```{r}
# fix mistake
evictions_la$Date.Received <- gsub("2205", "2025", evictions_la$Date.Received)

>>>>

## Number of Evictions and Crime Levels Per Month
```{r, echo=FALSE}
# fix mistake
evictions_la$Date.Received <- gsub("2205", "2025", evictions_la$Date.Received)
